Constructing the transition graphs of interacting hysterons

### 2022-05-18 Paper_draft.tex
Changed title
Fixed float specifiers
Fixed notation of switching fields

\title{Methods for constructing the transition graphs of an interacting hysteron model}
\author{Margot Teunisse}
\author{Martin van Hecke}%
\affiliation{%
Universiteit Leiden
}%

@@

    U_i^{+, -}(S) = U_i^{+, -} + \Delta u_i(S)

@@

Fortunately, it is not necessary to sample all of parameter space. The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $I_i^{+,-}(S)$, but only on the order of the switching fields. In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\

@@

    u_i^+(S) = \min_{s_j=0}u_j^+(S)

@@

    u_i^-(S) = \max_{s_j=1}u_j^-(S)

@@

We now observe that, because we only consider the switching fields $u_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable. Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche. As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips ($l=1$), then evaluating the possible avalanches for each graph in turn. We refer to the graphs with only $l=1$ transitions as base graphs.\\
\begin{figure}[!h]

@@

\begin{figure}[!h]

@@

\begin{figure}[h!]

@@

We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2. In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $u_2^+(00) < u_1^+(01)$. Next, we must have that the state 01 is stable under the current driving, which is the switching field $u_2^+(00)$. The requirement for state 01 to be stable leads to two more inequalities, namely $u_1^+(01) > u_2^+(00)$ and $u_2^-(01) < u_2^+ (00)$.\\
As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$. Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $u_2^-(11) > u_1^-(10)$. Next, a set of inequalities is required which describes the stability of the state 10 under the field $u_2^-(11)$. Unlike in the previous example, however, hysteron 1 must now be unstable. Thus, we obtain the set of inequalities $u_1^-(10) \geq u_2^-(11)$ and $u_2^+(10) > u_2^-(11)$\\

@@

    u_i^+(S^{(0)} = \min_{s_j = 0}u_j^+(S^{(0)})

@@

    u_i-(S^{(0)} = \max_{s_j = 1}u_j^-(S^{(0)})

@@

We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $u_i^{+, -}(S)$ depend on the state $S$ as:

@@

    u_i^{+, -}(S) = u_{i, 0}^{+, -} -\sum_{i \neq j}c_{ij}s_j

@@

\begin{figure}[!h]
    \includegraphics[width=0.5\textwidth]{.png}
    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
    \label{fig:linear_coupling}

@@

\bibliography{apssamp}% Produces the bibliography via BibTeX.

>>>>

\title{Constructing the transition graphs of interacting hysterons}
\author{Margot Teunisse}
\author{Martin van Hecke}%
\affiliation{%
Universiteit Leiden
}%

@@

    U_i^{+, -}(S) = u_i^{+, -} + \Delta u_i(S)

@@

Fortunately, it is not necessary to sample all of parameter space. The reason for this is that the transition graph for a given system does not depend on the absolute values of the switching fields $U_i^{+,-}(S)$, but only on the order of the switching fields. In principle, one could find all possible transition graphs for a given number of hysterons $N$ by evaluating all permutations of the order of the switching fields.\\

@@

    U_i^+(S) = \min_{s_j=0}U_j^+(S)

@@

    U_i^-(S) = \max_{s_j=1}U_j^-(S)

@@

We now observe that, because we only consider the switching fields $U_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable. Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche. As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips ($l=1$), then evaluating the possible avalanches for each graph in turn. We refer to the graphs with only $l=1$ transitions as base graphs.\\
\begin{figure}[!ht]

@@

\begin{figure}[!ht]

@@

\begin{figure}[ht!]

@@

We first consider the inequalities required for the transition $00\uparrow 01$, which consists out of a single flip of hysteron 2. In order for hysteron 2 to flip before hysteron 1 when the driving $U$ is increased, one must have that $U_2^+(00) < U_1^+(01)$. Next, we must have that the state 01 is stable under the current driving, which is the switching field $U_2^+(00)$. The requirement for state 01 to be stable leads to two more inequalities, namely $U_1^+(01) > U_2^+(00)$ and $U_2^-(01) < U_2^+ (00)$.\\
As a second example, we consider the avalanche $11\downarrow 10 \downarrow 00$. Analogously to the previous example, we first require for hysteron 2 to be the first to flip down when decreasing the driving $U$, so that we obtain the inequality $U_2^-(11) > U_1^-(10)$. Next, a set of inequalities is required which describes the stability of the state 10 under the field $U_2^-(11)$. Unlike in the previous example, however, hysteron 1 must now be unstable. Thus, we obtain the set of inequalities $U_1^-(10) \geq U_2^-(11)$ and $U_2^+(10) > U_2^-(11)$\\

@@

    U_i^+(S^{(0)} = \min_{s_j = 0}U_j^+(S^{(0)})

@@

    U_i-(S^{(0)} = \max_{s_j = 1}U_j^-(S^{(0)})

@@

We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:

@@

    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j

@@

%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\

@@

%\bibliography{apssamp}% Produces the bibliography via BibTeX.
